% First paragraph
I am writing to you to express my interest in the
\say{Software Engineer, Content Platform} position this summer.
I am excited to apply for Blizzard because StarCraft 2 is one of
the few games that are still able to capture my heart since I played
it for the first time since primary school.

% Second paragraph
I am most interested in contributing to the content platform as a full
stack developer. I started my full-stack experience
when I took the honor section of \say{Intro to Computer Science} at my
University. Since then, I have fallen in love with React.js because of
how easy it is to understand its internal workings.
Also, my coursework at the university has given me a solid
experience with C++ and Java and the game-related projects that I have worked
on made me know C\# well.
These experiences,
combined with my experience in developing game-related projects and
myself being a fast and effective learner,
in my opinion, makes me a good candidate for this position.

% Third paragraph
Since my introduction to full-stack development, I have always tried to
understand the internals of Node.js and what makes it scales well,
and in a system-programming course that I took this semester, my professor went
over concepts like multitasking, epoll and non-blocking IO that
have further sparked my interest in servers
that can operate on a large scale.
This internship opportunity is what I have been looking for to
be able to gain more insights into full-stack development,
prepare me for the backend sector of the gaming industry,
and ultimately help me decide the next chapter of my life after an
undergraduate degree.
