% First paragraph
I am writing to you to express my interest in the
\say{Software Engineer Intern, Game Websites} position this summer.
I am excited to apply for Blizzard because StarCraft 2 is one of
the few games that are still able to capture my heart since I played
it for the first time since primary school.

% Second paragraph
I am most interested in developing beautiful and performant frontend
applications. I started to develop frontend applications
when I took the honor section of \say{Intro to Computer Science} at my
University. Since then, I have fallen in love with React.js because of
how easy it is to understand its internal workings.
I have worked on numerous personal or University projects using React.js
that I believe have given me the qualifications for this position, such as
React, CSS, and HTML and being able to work in a team environment.
This, combined with my experience in developing game-related projects and
myself being a fast and effective learner,
in my opinion, makes me a good candidate for this position.

% Third paragraph
The desire to improve people's lives by making the frontend more
intuitive and comparable to desktop experience has always motivated
me from project to project.
This internship opportunity is what I have been looking for to
be able to reach and impact the lives of gamers around the world,
prepare me for the frontend sector of the gaming industry,
and ultimately help me decide the next chapter of my life after an
undergraduate degree.
